POSTER: \da :\\Measuring the security of smartphones

### 2015-04-24 wisec2015abstract.tex
Add pagenumbering to wisec abstract
Add bibliography to wisec abstract

\documentclass{sig-alternate}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}

@@

\section{Privacy Concerns}
We plan to periodically release the collected anonymous dataset where participants have given us permission to do so.
This raises privacy concerns that need to be addressed before such a comprehensive and potentially invasive dataset can be released.
As a first measure we will only publish data that was collected at least three months ago, giving participants time to view the data they contributed.
If they are concerned about having their data released they can opt-out of any further data collection and erase all unpublished data from our server.
Furthermore, while physical location of participants could be an asset of our dataset, such data would need to be handled with great care, as disclosure of even approximate home/work location pairs could lead to deanonymization of participants [2].

>>>>

\documentclass{sig-alternate}
\pagenumbering{arabic}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}

\RequirePackage[date=terse, isbn=true, doi=true, url=false, urldate=iso8601, maxbibnames=9, backref=false, backend=bibtex, style=ieee]{biblatex}
\addbibresource{securityupdates.bib}
\renewcommand{\bibfont}{\small}

\AtEveryBibitem{% Clean up the bibtex rather than editing it
 \clearname{editor} % remove editors
}

@@

\section{Privacy Concerns}
We plan to periodically release the collected anonymous dataset where participants have given us permission to do so.
This raises privacy concerns that need to be addressed before such a comprehensive and potentially invasive dataset can be released.
As a first measure we will only publish data that was collected at least three months ago, giving participants time to view the data they contributed.
If they are concerned about having their data released they can opt-out of any further data collection and erase all unpublished data from our server.
Furthermore, while physical location of participants could be an asset of our dataset, such data would need to be handled with great care, as disclosure of even approximate home/work location pairs could lead to deanonymization of participants~\cite{Golle2009}.
